%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage[backend=biber]{biblatex}
\addbibresource{bib.bib} % Specify the bibliography file to include publications
\usepackage{aas_macros}

\begin{document}

\header{Samuel}{ Hinton}{B.E. Software Engineering (Hon), B.Sc Physics (Hon)} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
30 Matingara St
Chapel Hill, QLD 4069
Australia
~
+61 424 670 574
~
\href{mailto:samuelreay@gmail.com}{samuelreay@gmail.com}
\href{https://github.com/samreay}{Github}
\href{https://Samreay.github.io}{Personal}
~
References available on request.
~
\section{Programming}
JavaScript,
HTML5 \& CSS3
Python, Java
C, C++
Matlab
SQL, LaTeX
~
Bash, SVN
Git, Maven
Node.js, AngularJS
~
\section{Interests}
astrophysics
cosmology 
 computational physics 
  science communication 
   software design 
~
\section{Communication}
\textit{2010}
Professional Tutoring
\textit{2014}
Physics Review Representative
\textit{2015}
College Tutoring
Honours student address
High school astronomy talk 
\textit{2016}
University Tutoring
Science Demo Troupe
\end{aside}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2010--2015}
{Bachelor of Engineering {\normalfont (Software)}}
{University of Queensland}
{Awarded 1\textsuperscript{st} class honours and graduated top of engineering cohort. Undergraduate engineering thesis entailed writing the web-application \textsc{Marz} to redshift spectra from the AAOmega spectrograph for the OzDES team. }
\entry
{2010--2016}
{Bachelor of Science {\normalfont (Physics)}}
{University of Queensland}
{Awarded 1\textsuperscript{st} class honours and graduated top of science cohort. Thesis project investigated the 2D BAO signal found in the final Wigglez dataset to constrain cosmological parameters.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
%\vspace{10mm}
\section{Experience}

\begin{entrylist}
%------------------------------------------------
%\entry{2015}{St John's College}{Brisbane, Queensland, Australia}{\emph{Tutor}\\Tutored first, second and third year students in the areas of physics and software engineering several times a week.}
%\entry{2014--2015}{UQ}{Brisbane, Queensland, Australia}{\emph{Summer Research Scholarship} \\Theoretical cosmology research over the summer break. Close collaboration with Chris Lidman (AAO), Chris Blake (Swinburne) and the OzDES researchers at ANU.}
\entry
{2010--2014}
{GBST}
{Brisbane, Queensland, Australia}
{\emph{Software Developer} \\
Developed business intelligence reporting solutions for clients, designing and developing server and client based web application code, creation of large scale SQL queries, experience optimising queries, databases and applications for network, processing and memory constraints, developed back-end server code and front-end web applications. Prioritised implementation tasks for strict release schedules, delegated work tasks for other developers and reviewed incoming work for quality.}

\entry
{2015--2016}
{Gemini \& Australian Astronomical Observatory}
{La Serena, Chile}
{\emph{Research Intern} \\
	Internship for the Australian Gemini Undergraduate Summer Studentship. Utilised photometric data of Maffei 1 to determine globular cluster candidates and their properties for spectroscopic follow-up. Utilised data reduction pipelines, automated analysis methods in Python, and applied machine learning techniques to perform object classification.}


\entry
{2016--Now}
{Lawrence Berkeley National Laboratory}
{Berkeley, California}
{\emph{Research Fellowship} \\
	Research fellowship at LBNL to work on Bayesian Hierarchical Modelling and its applications to Supernova Cosmology. Specifically, investigating how to use high dimensional hierarchical models to model individual supernova instead of populations to provide better constraints on cosmology using supernova discovered by the Dark Energy Survey.}


%\entry
%{2010--2011}
%{SummitTuition}
%{Brisbane, Queensland, Australia}
%{\emph{Tutor} \\
%Tutoring individual and small groups of students in senior subjects, primarily in Physics, Mathematics C, Mathematics B, Graphical Drafting, Business Graphics and English.}
\end{entrylist}
%\vspace{10mm}




%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\section{Recent Awards}
\begin{entrylist}
\entry
{2016}
{University Medal (Science)}
{University of Queensland}
{Awarded in recognition of outstanding academic success.}
\end{entrylist}
\begin{entrylist}
	\entry
{2016}
{Bok Prize}
{Astronomical Society of Australia}
{Recognising outstanding research in astronomy by an Honours student or eligible Masters student over all Australian universities.}
\end{entrylist}
\begin{entrylist}
	\entry
{2016}
{Australian Postgraduate Award}
{Australian Government}
{A PhD scholarship awarded to students of exceptional research potential.}
\end{entrylist}
\begin{entrylist}
	\entry
{2015}
{Australian Gemini Undergraduate Summer Studentships}
{AAO}
{Studentship at the Gemini South telescope awarded to 3 Australian students.}
\end{entrylist}
\begin{entrylist}
\entry
{2015}
{A.W. Oakes Scholarship}
{St John's College}
{Awarded to an honours student of outstanding academic success and research potential.}
\end{entrylist}
\begin{entrylist}
\entry
{2015}
{AAO Honours Scholarship}
{Australian Astronomical Observatory}
{Awarded to an honours student undertaking a research project co-supervised by an AAO staff-member.}
\end{entrylist}
\begin{entrylist}
\entry
{2015}
{Harriet Marks Bursary}
{University of Queensland}
{Awarded to an science honours student for academic merit.}
\end{entrylist}
\begin{entrylist}
\entry
{2014}
{University Medal (Engineering)}
{University of Queensland}
{Awarded in recognition of outstanding academic success.}
\end{entrylist}
\begin{entrylist}
\entry
{2014}
{David Andrew Krnak Memorial Prize}
{University of Queensland}
{Awarded to the top graduating engineering student for outstanding academic performance.}
\end{entrylist}
\begin{entrylist}
\entry
{2014}
{UQ Future Leader}
{University of Queensland}
{Recognises graduating students who have gone beyond their typical program of studies to make a positive impact on campus and community.}
\end{entrylist}
\begin{entrylist}
\entry
{2014}
{IEEE Student Thesis Prize}
{IEEE}
{Awarded for the best final year thesis in all fields of electric engineering and information technology.}
\end{entrylist}
\begin{entrylist}
\entry
{2014}
{IET Student Prize}
{The Institution of Engineering and Technology}
{Awarded to a student of outstanding academic accomplishment at the end of their degree.}
\end{entrylist}
\begin{entrylist}
\entry
{2014}
{GroundProbe Prize}
{University of Queensland}
{Awarded for best thesis project in microwave, photonics \& communications..}
\end{entrylist}


\section{Other Awards}
\begin{entrylist}
	\entryInlineSmall
	{2015}
	{Australian Institute of Physics Prize}
	{UQ}
	{Awarded to top performing student completing physics honours.}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2015}
	{Rhodes Scholarship Finalist}
	{Oxford University}
	{}
\end{entrylist}
\begin{entrylist}
\entryInlineSmall
{2015}
{10x Deans Commendation}
{UQ}
{Awarded to students with outstanding academic results over a semester, achieved every semester.}
\end{entrylist}
\begin{entrylist}
\entryInlineSmall
{2015}
{Helen Thompson Prize for All Round Excellence}
{St John's College}
{Excellence and outstanding contribution to academic and college life.}
\end{entrylist}
\begin{entrylist}
	\entryInline
	{2014}
	{RWH Hawken Scholar}
	{UQ}
	{(2010--2014) Awarded to highly performing students}
\end{entrylist}
\begin{entrylist}
\entryInlineSmall
{2014}
{UQ Summer Research Scholarship}
{UQ}
{}
\end{entrylist}
\begin{entrylist}
\entryInline
{2012}
{Exxon Mobil Achievement Award}
{UQ}
{Top mechanical engineering student.}
\end{entrylist}
\begin{entrylist}
\entryInline
{2011}
{Alstom Prize}
{UQ}
{Top electrical engineering student.}
\end{entrylist}
\begin{entrylist}
\entryInline
{2011}
{Walter Bruce Darker Scholarship}
{UQ}
{Top 3rd year engineering student.}
\end{entrylist}
\begin{entrylist}
\entryInlineSmall
{2010}
{UQ Academic Excellence Scholarship}
{UQ}
{A four year scholarship awarded to students demonstrating high academic ability.}
\end{entrylist}
\begin{entrylist}
\entryInlineSmall
{2010}
{ICT Enabling Scholarship}
{UQ}
{A one year scholarship awarded to students who have demonstrated outstanding Information and Communications Technology skills.}
\end{entrylist}
\begin{entrylist}
\entryInline
{2010}
{John Black Prize}
{UQ}
{Highest performing first year male.}
\end{entrylist}
\begin{entrylist}
\entryInline
{2009}
{OP1}
{QTAC}
{Highest possible secondary education exit score.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Publications}


\printbibsection{article}{Articles} % Print all articles from the bibliography


%\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

%\printbibsection{report}{research reports} % Print all research reports from the bibliography
%\begin{entrylist}
%------------------------------------------------

%------------------------------------------------
%\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------



%%%
%\clearpage
%\section{Referees}
%
%\begin{entrylist}
%%------------------------------------------------
%\entry
%{Cosmology}
%{Prof. Tamara Davis}
%{Physics Department, University of Queensland}
%{Tamara Davis is an Australian Research Council Future Fellow and researches fundamental physics, such as the properties of dark matter and dark energy. Contactable on 0432 526 989.}
%%------------------------------------------------
%\end{entrylist}
%%------------------------------------------------
%\begin{entrylist}
%\entry
%{Cosmology}
%{Prof. Michael Drinkwater}
%{Physics Department, University of Queensland}
%{Michael Drinkwater obtained his PhD in Cambridge and currently holds position in the University of Queensland's Physics Department as a Professor of Astrophysics. Contactable on 0432 887 642.}
%%------------------------------------------------
%\end{entrylist}
%
%\begin{entrylist}
%%------------------------------------------------
%\entry
%{Software}
%{James Cordwell}
%{Business Reporting Specialist, GBST}
%{James Cordwell is the Business Intelligence Reporting product owner within GBST. Contactable on 0401 976 228.}
%%------------------------------------------------
%\end{entrylist}

%----------------------------------------------------------------------------------------



\end{document}