\documentclass[]{friggeri-cv2}
\input{includes}

\begin{document}
\pagestyle{plain}

\header{Samuel}{ Hinton}{, PhD}{Data Scientist | Software Engineer | Astrophysicist}


\begin{aside}
\section{Links}
\href{https://cosmiccoding.com.au}{Website: CosmicCoding}
\href{https://www.linkedin.com/in/samuelreay/}{LinkedIn: samuelreay}
\href{https://github.com/samreay}{GitHub: samreay}
\section{Skills}
Python, C, golang, Javascript, SQL, Java, Stan, Git
Machine learning
Numerical Optimisation
Visualisation
Bayesian Statistics
Model fitting
\section{Awards}
Nobel Laureate Delegate
UQ Future Superstar
ASA Bok Prize
Science Grad. of the Year
AIP Prize
University Medal (Science)
University Medal (Eng.)
AAO Honours Scholarship
A.W. Oakes Scholarship
Harriet Marks Bursary
Helen Thompson Prize
IET Student Prize
David Andrew Krnak Prize
UQ Future Leader
IEEE Student Prize
GroundProbe Prize
RWH Hawken Scholar
Alstom Prize
John Black Prize
\section{Communication}
Numerous podcast appearances.
~
Academic presentations in more than a dozen institutions and countries.
~
Science outreach appearances on multiple TV shows, radio channels and public events.
\section{Publications}
6 first author
100+ contributing author
Areas of software, statistics, astrophysics, medicine.
\end{aside}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
%\vspace{10mm}
\section{Experience}

\begin{entrylist}

\entry
{2020-Now}
{Arenko Group}
{London, UK}
{\emph{Senior Data Scientist} \\
Designed and productionised \highlight{probabilistic time-series forecasting} models for \textcolor{red}{UK} energy markets.
Implemented \highlight{MLOps} pipelines in AWS, including feature store, model versioning (mlflow), model serving, 
\highlight{data engineering} and orchestration (Prefect) and digestion (RDMS) in a microservice framework.
Created library of transformations, models, and utilities in Python.
Created interactive \highlight{visualisations} of market opportunities (matplotlib, plotly, Dash, angular).
Mentored junior data scientists and helped grow the data science team.}

\entry
{2020}
{University of Queensland}
{Brisbane, Queensland, Australia}
{\emph{Lead Data Analyst} \\
Created a \highlight{data science pipeline} for the COVID-19 Critical Care Consortium. 
Homogenised and standardised heterogeneous medical data for eventual use in causal modelling. 
Created reports, dashboards, and products as support for clinical staff.}

\entry
{2016-2020}
{University of Queensland}
{Brisbane, Queensland, Australia}
{\emph{Astrophysicist} \\
Created \highlight{data pipelines} to run from data preparation to classification, modelling and reports. 
Created \highlight{machine learning classifiers} to discriminate between supernova. 
Applied \highlight{high-dimensional modelling} techniques on astrophysical problems.
Organised a team of two dozen researchers across multiple countries.}

%\entry
%{2019-Now}
%{SuperDataScience}
%{Sunshine Coast, Queensland, Australia}
%{\emph{Course Instructor} \\
%Created courses on statistical analysis and data manipulation in Python for students. 
%Focused on applied statistics and utilisation of modern code packages.}

\entry
{2017, 2016}
{Lawrence Berkeley National Laboratory}
{Berkeley, California}
{\emph{Research Fellowship} \\
High-dimensional \highlight{Bayesian Hierarchical Modelling} for Supernova Cosmology. 
Involved using numerous \highlight{MCMC} fitters, Stan, Gaussian processes and many numerical techniques.}


%\entry
%{2015--2016}
%{Gemini \& Australian Astronomical Observatory}
%{La Serena, Chile}
%{\emph{Research Intern} \\
%Reduced telescope data and utilised engineered features to classify globular cluster candidates and their properties for follow up with the Hubble Space Telescope.}

\entry
{2010--2014}
{GBST}
{Brisbane, Queensland, Australia}
{\emph{Software Developer} \\
Developed \highlight{business intelligence reports} and user-facing applications (angular, Java) 
for front office financial traders. Created and optimised large scale \highlight{SQL} queries. 
Optimised \highlight{databases} and applications for network, processing, and memory constraints.}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
\entry
{2016--2020}
{Doctor of Philosophy}
{University of Queensland}
{Thesis: Analysed supernovae in the Dark Energy Survey using Hierarchical Bayesian models to constrain the nature of dark energy.}
\entry
{2010--2015}
{Bachelor of Science {\normalfont (Physics)(Hons, 1\textsuperscript{st})}}
{University of Queensland}
{Thesis: Analysed the Baryon Acoustic Oscillation signal imprinted in the large scale structure of the universe.}
\entry
{2010--2014}
{Bachelor of Engineering {\normalfont (Software)(Hons, 1\textsuperscript{st})}}
{University of Queensland}
{Thesis: Created the first online client-only web application to compute redshifts from telescope spectra. }
\end{entrylist}
\end{document}

