\documentclass[]{friggeri-cv2}
\input{includes}

\begin{document}
\pagestyle{plain}

\header{Samuel}{ Hinton}{, PhD}{Data Scientist | Software Engineer | Astrophysicist}


\begin{aside}
\section{Links}
\href{https://cosmiccoding.com.au}{Website: CosmicCoding}
\href{https://www.linkedin.com/in/samuelreay/}{LinkedIn: samuelreay}
\href{https://github.com/samreay}{GitHub: samreay}
\section{Skills}
Python, C, Javascript, SQL, Java, Stan, Git
Machine learning
Numerical Optimisation
Visualisation
Bayesian Statistics
Model fitting
\section{Awards}
Nobel Laureate Delegate
UQ Future Superstar
ASA Bok Prize
Science Grad. of the Year
AIP Prize
University Medal (Science)
University Medal (Eng.)
AAO Honours Scholarship
A.W. Oakes Scholarship
Harriet Marks Bursary
Helen Thompson Prize
IET Student Prize
David Andrew Krnak Prize
UQ Future Leader
IEEE Student Prize
GroundProbe Prize
RWH Hawken Scholar
Alstom Prize
John Black Prize
\section{Communication}
Numerous podcast appearances.
~
Academic presentations in more than a dozen institutions and countries.
~
Science outreach appearances on multiple TV shows, radio channels and public events.
\section{Publications}
6 first author
75+ contributing author
Areas of software, statistics, astrophysics, medicine.
\end{aside}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
%\vspace{10mm}
\section{Experience}

\begin{entrylist}

\entry
{2020-Now}
{Arenko Group}
{London, UK}
{\emph{Senior Data Scientist} \\
Implemented MLOps pipelines for data engineering, model versioning and productionising code. Implemented ML models to predict energy markets, and created algorithms to utilise market predictions to produce optimal profit.}
\entry
{2020}
{University of Queensland}
{Brisbane, Queensland, Australia}
{\emph{Lead Data Analyst} \\
Created a data science pipeline for the COVID-19 Critical Care Consortium. Homogenised and standardised heterogeneous medical data for eventual use in causal modelling. Created reports, dashboards, and products as support for clinical staff.}
\entry
{2016-2020}
{University of Queensland}
{Brisbane, Queensland, Australia}
{\emph{Astrophysicist} \\
Created data pipelines to run from data preparation to, classification, modelling and reports. Created classifiers to discriminate between supernova. Applied high-dimensional modelling techniques on the large-scale-structure in the universe.}
\entry
{2019-Now}
{SuperDataScience}
{Sunshine Coast, Queensland, Australia}
{\emph{Course Instructor} \\
Created courses on statistical analysis and data manipulation in Python for students. Focused on applied statistics and utilisation of modern code packages.}
\entry
{2017, 2016}
{Lawrence Berkeley National Laboratory}
{Berkeley, California}
{\emph{Research Fellowship} \\
High-dimensional Bayesian Hierarchical Modelling for Supernova Cosmology. Involved using numerous MCMC fitters, Stan, Gaussian processes and many numerical techniques.}


%\entry
%{2015--2016}
%{Gemini \& Australian Astronomical Observatory}
%{La Serena, Chile}
%{\emph{Research Intern} \\
%Reduced telescope data and utilised engineered features to classify globular cluster candidates and their properties for follow up with the Hubble Space Telescope.}

\entry
{2010--2014}
{GBST}
{Brisbane, Queensland, Australia}
{\emph{Software Developer} \\
Developed business intelligence reporting solutions, designed and developed server and client based web application code, creation of large scale SQL queries. Optimised queries, databases, and applications for network, processing, and memory constraints. Developed back-end server code and front-end web applications, plus API's to connect the two.}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
\entry
{2016--2020}
{Doctor of Philosophy}
{University of Queensland}
{Analysing supernovae in the Dark Energy Survey using Hierarchical Bayesian models to help constrain the nature of dark energy.}
\entry
{2010--2015}
{Bachelor of Science {\normalfont (Physics)(Hons, 1\textsuperscript{st})}}
{University of Queensland}
{Thesis: Analysed the Baryon Acoustic Oscillation signal imprinted in the large scale structure of the universe.}
\entry
{2010--2014}
{Bachelor of Engineering {\normalfont (Software)(Hons, 1\textsuperscript{st})}}
{University of Queensland}
{Thesis: Created the first online client-only web-application to compute redshifts from telescope spectra. }
\end{entrylist}
\end{document}

