\documentclass[11pt]{friggeri-cv}

\newcommand{\seps}{$\ \textcolor{lightergray}{\bullet} \ \ $}
\input{includes}

\begin{document}
\pagestyle{plain}

\header{Samuel}{ Hinton}{Data Scientist | Software Engineer | Astrophysicist}

\section{Contact}

\textbf{Email: } \href{samuelreay@gmail.com}{samuelreay@gmail.com}   \hspace{1mm}
%\textbf{Phone: } +61 424 670 574      \hspace{1mm}
\textbf{Website: } \href{https://cosmiccoding.com.au}{https://cosmiccoding.com.au}   
\textbf{LinkedIn: } \href{https://www.linkedin.com/in/samuelreay/}{samuelreay}



\section{Education}

\begin{entrylist}
\entry
{2016--2020}
{Doctor of Philosophy}
{University of Queensland}
{Bayesian statistics, hierarchical modelling of exploding stars, data and machine learning pipelines to streamline scientific analyses.}
\entrysmall
{2010--2015}
{Bachelor of Science {\normalfont (Physics)(Hons, 1\textsuperscript{st})}}
{University of Queensland}
{}%{Thesis: Analysed the Baryon Acoustic Oscillation signal imprinted in the large scale structure of the universe.}
\entrysmall
{2010--2014}
{Bachelor of Engineering {\normalfont (Software)(Hons, 1\textsuperscript{st})}}
{University of Queensland}
{}%{Thesis: Created the first online client-only web-application to compute redshifts from telescope spectra. }
\end{entrylist}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
%\vspace{10mm}
\section{Experience}

\begin{entrylist}
\entry
{12/2020-Now}
{Data Scientist | Arenko Group}
{London, UK}
{\emph{Full-time} \\
Implemented MLOps pipelines for model versioning and productionising. Implemented ML models to predict energy markets, and created algorithms to utilise market predictions to produce optimal profit.}
\entry
{03/2020 - 09/2020}
{Lead Data Analyst | University of Queensland}
{Brisbane, Queensland, Australia}
{\emph{Part-time} \\
Created a data science pipeline for the COVID-19 Critical Care Consortium. Homogenised and standardised heterogeneous medical data for eventual use in causal modelling. Created reports, dashboards, and data products as support for clinical staff.}
\entry
{03/2016 - 11/2020}
{Astrophysicist | University of Queensland}
{Brisbane, Queensland, Australia}
{\emph{Part-time} \\
Created data pipelines for international collaborations to run from data preparation to classification, modelling and reports. Created classifiers to discriminate between supernova. Applied high-dimensional modelling techniques on the large-scale-structure in the universe.}
\entry
{04/2019 - Now}
{Course Instructor | SuperDataScience}
{Sunshine Coast, Queensland, Australia}
{\emph{Casual Contract} \\
Created courses on statistical analysis and data manipulation in Python for students. Focused on applied statistics and utilisation of modern code packages, with attention given to visual output and workflows for continuous validation of methodology.}
\entry
{Summer 2017}
{Student Research Fellowship | Lawrence Berkeley Laboratory}
{ California}
{ \emph{Full-time} \\
Solved the challenge of fitting high-dimensional astrophysical models using advanced numerical techniques, allowing more robust calculation of model uncertainty.}
\end{entrylist}
\begin{entrylist}
\entry
{11/2015 - 02/2016}
{Research Intern | Gemini \& Australian Astronomical Observatory}
{Chile}
{\emph{Full-time} \\
Reduced telescope data, engineered features, and applied machine learning techniques to classify extra-galactic candidates for follow up with the Hubble Space Telescope.}
\end{entrylist}
\begin{entrylist}
\entry
{06/2010 - 09/2014}
{Software Developer | GBST}
{Brisbane, Queensland, Australia}
{\emph{Part-time} \\
Developed business intelligence reporting solutions for brokerage clients. Designed and developed server and client based web application code, creation of large scale SQL queries. Optimised queries, databases, and applications. Developed back-end server code and front-end web applications to improve reporting.}

\end{entrylist}




\section{Noteable Awards}
\begin{entrylist}
	\wentryInline
	{2019} % Feb 06
	{Lindau Nobel Laureate Delegate}
	{Australian Academy of Science}
	{Aus rep at LINO19.}
\end{entrylist}
\begin{entrylist}
	\wentryInline
	{2019} % Feb 06
	{Future Superstar Award}
	{University of Queensland}
	{Highest performing PhD student.}
\end{entrylist}
\begin{entrylist}
	\wentryInline
	{2016} % April 27
	{Bok Prize}
	{Astronomical Society of Australia}
	{Best astrophysics honours thesis in Australia.}
\end{entrylist}
\begin{entrylist}
	\wentryInlineSmall
	{2016} % Jan 7
	{Australian Postgraduate Award}
	{Australian Government}
	{A PhD scholarship awarded to students of exceptional research potential.}
\end{entrylist}
\begin{entrylist}
	\wentryInlineSmall
	{2016} % June 6
	{Science Faculty Graduate of the Year}
	{University of Queensland}
	{}
\end{entrylist}
\begin{entrylist}
	\wentryInline
	{2016} % Feb 22 
	{Australian Institute of Physics Prize}
	{University of Queensland}
	{Top physics graduate.}
\end{entrylist}
\begin{entrylist}
	\wentryInlineSmall
	{2016} % May 19
	{University Medal (Science)}
	{University of Queensland}
	{Awarded in recognition of outstanding academic success.}
\end{entrylist}
\begin{entrylist}
	\wentryInlineSmall
	{2015} % May 14
	{University Medal (Engineering)}
	{University of Queensland}
	{Awarded in recognition of outstanding academic success.}
\end{entrylist}
\vspace{-5mm}

Other awards available on request.

\section{Skills}

\begin{entrylist}
\wbindent{Languages:}{Python,  C,  C++,  Javascript,  SQL,  Java,  Stan,  Git.\vspace{3mm}}
\wbindent{Techniques:}{Machine learning,  Numerical Optimisation,  Visualisation,  Bayesian Statistics,  Model discrimination,  Pipelines.}
\wbindent{Communication:}{Numerous podcast appearances in areas of Data Science, comedy, astrophysics, reality TV. Experience communicating complex topics effectively in radio, TV (recorded + live), public lectures and presentations. }
\wbindent{Publications:}{6 first author, 75+ contributing author. Areas of software, statistics, astrophysics, medicine.}
\end{entrylist}
% \section{References}
% 
% \begin{entrylist}
% 	\bindent{Prof. Tamara Davis:}{\textit{+61 432 526 989},\hspace{5mm} \href{mailto:tamarad@physics.uq.edu.au}{tamarad@physics.uq.edu.au} \vspace{3mm}}
% 	\bindent{Dr Sally Shrapnel:}{\textit{+61 437 549 124},\hspace{5mm} \href{mailto:s.shrapnel@uq.edu.au}{s.shrapnel@uq.edu.au}}
% \end{entrylist}



\end{document}

