%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage[backend=biber]{biblatex}
\addbibresource{bib_primary.bib} % Specify the bibliography file to include publications
\addbibresource{bib_secondary.bib} % Specify the bibliography file to include publications
\addbibresource{bib_draft.bib} % Specify the bibliography file to include publications
\usepackage{aas_macros}


\def\makenamesetup{%
  \def\bibnamedelima{~}%
  \def\bibnamedelimb{ }%
  \def\bibnamedelimc{ }%
  \def\bibnamedelimd{ }%
  \def\bibnamedelimi{ }%
  \def\bibinitperiod{.}%
  \def\bibinitdelim{~}%
  \def\bibinithyphendelim{.-}}
\newcommand*{\makename}[2]{\begingroup\makenamesetup\xdef#1{#2}\endgroup}

\newcommand*{\boldname}[3]{%
  \def\lastname{#1}%
  \def\firstname{#2}%
  \def\firstinit{#3}}
\boldname{}{}{}

% Patch new definitions
\renewcommand{\mkbibnamegiven}[1]{%
  \ifboolexpr{ test {\ifdefequal{\lastname}{\namepartfamily}} }
  {\mkbibbold{#1}}{#1}%
}

\renewcommand{\mkbibnamefamily}[1]{%
  \ifboolexpr{ test {\ifdefequal{\lastname}{\namepartfamily}} }
  {\mkbibbold{#1}}{#1}%
}

\boldname{Hinton}{Samuel}{S}

\begin{document}

\header{Samuel}{ Hinton}{PhD Candidate, samuelreay@gmail.com} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2016--Now}
{Doctor of Philosophy}
{University of Queensland}
{Analysing supernovae in the Dark Energy Survey using Hierarchical Bayesian models to help constrain the nature of dark energy.}
\entry
{2010--2015}
{Bachelor of Science {\normalfont (Physics)(Hons, 1\textsuperscript{st})}}
{University of Queensland}
{Thesis: Analysed the Baryon Acoustic Oscillation signal imprinted in the large scale structure of the universe using the WiggleZ survey. Won the Astronomical Society of Australia's award for best Australian Astrophysics honours thesis of the year.}
\entry
{2010--2014}
{Bachelor of Engineering {\normalfont (Software)(Hons, 1\textsuperscript{st})}}
{University of Queensland}
{Thesis: Created the first online client-only web-application to compute redshifts from telescope spectra. Won the GroudProbe prize, IEEE student thesis prize and IET student prize.}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
%\vspace{10mm}
\section{Experience}

\begin{entrylist}
%------------------------------------------------
%\entry{2015}{St John's College}{Brisbane, Queensland, Australia}{\emph{Tutor}\\Tutored first, second and third year students in the areas of physics and software engineering several times a week.}
%\entry{2014--2015}{UQ}{Brisbane, Queensland, Australia}{\emph{Summer Research Scholarship} \\Theoretical cosmology research over the summer break. Close collaboration with Chris Lidman (AAO), Chris Blake (Swinburne) and the OzDES researchers at ANU.}

\entry
{2019}
{SuperDataScience}
{Sunshine Coast, Queensland, Australia}
{\emph{Course Instructor} \\
Created a course on statistical analysis in Python for students. Focused on applied statistics and utilisation of modern code packages, with attention given to visual output and workflows for continuous validation of methodology.}
\entry
{2017, 2016}
{Lawrence Berkeley National Laboratory}
{Berkeley, California}
{\emph{Research Fellowship} \\
	Research fellowship to work on Bayesian Hierarchical Modelling and its applications to Supernova Cosmology. Specifically, investigating how to use high dimensional hierarchical models to model individual supernova instead of populations to provide better constraints on cosmology using supernova discovered by the Dark Energy Survey.}


\entry
{2015--2016}
{Gemini \& Australian Astronomical Observatory}
{La Serena, Chile}
{\emph{Research Intern} \\
Utilised photometric data of Maffei 1 to determine globular cluster candidates and their properties for spectroscopic follow-up. Utilised data reduction pipelines, automated analysis methods in Python, and applied machine learning techniques to perform object classification.}

\entry
{2010--2014}
{GBST}
{Brisbane, Queensland, Australia}
{\emph{Software Developer} \\
Developed business intelligence reporting solutions, designing and developing server and client based web application code, creation of large scale SQL queries, optimising queries, databases and applications for network, processing and memory constraints, developed back-end server code and front-end web applications.}


%\entry
%{2010--2011}
%{SummitTuition}
%{Brisbane, Queensland, Australia}
%{\emph{Tutor} \\
%Tutoring individual and small groups of students in senior subjects, primarily in Physics, Mathematics C, Mathematics B, Graphical Drafting, Business Graphics and English.}
\end{entrylist}
%\vspace{10mm}





\section{Noteable Awards}
\begin{entrylist}
	\entryInline
	{2019} % Feb 06
	{Lindau Nobel Laureate Delegate}
	{Australian Academy of Science}
	{Representing Australia at LINO19.}
\end{entrylist}
\begin{entrylist}
	\entryInline
	{2019} % Feb 06
	{Future Superstar Award}
	{University of Queensland}
	{Science's highest performing PhD student.}
\end{entrylist}
\begin{entrylist}
	\entryInline
	{2016} % April 27
	{Bok Prize}
	{Astronomical Society of Australia}
	{Best astrophysics honours thesis in Australia.}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2016} % Jan 7
	{Australian Postgraduate Award}
	{Australian Government}
	{A PhD scholarship awarded to students of exceptional research potential.}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2016} % June 6
	{Science Faculty Graduate of the Year}
	{University of Queensland}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInline
	{2016} % Feb 22 
	{Australian Institute of Physics Prize}
	{University of Queensland}
	{Top physics graduate.}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2016} % May 19
	{University Medal (Science)}
	{University of Queensland}
	{Awarded in recognition of outstanding academic success.}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2015} % Sep 4
	{Australian Gemini Undergraduate Summer Studentships}
	{Australian Astronomical Observatory}
	{Studentship at the Gemini South telescope awarded to 3 Australian students.}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2015} % March 19
	{AAO Honours Scholarship}
	{Australian Astronomical Observatory}
	{Awarded to an honours student undertaking a research project co-supervised by an AAO staff-member.}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2015} % May 14
	{University Medal (Engineering)}
	{University of Queensland}
	{Awarded in recognition of outstanding academic success.}
\end{entrylist}


\section{Other Awards}
\begin{entrylist}
	\entryInlineSmall
	{2015}
	{Rhodes Scholarship Finalist}
	{Oxford University}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2015} % Feb 18
	{A.W. Oakes Scholarship}
	{St John's College}
	{Awarded to an honours student of outstanding academic success and research potential.}
\end{entrylist}
\begin{entrylist}
	\entryInline
	{2015} % July 15
	{Harriet Marks Bursary}
	{University of Queensland}
	{Academic merit in science honours.}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2015}
	{10x Deans Commendation}
	{University of Queensland}
	{Awarded to students with outstanding academic results.}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2015}
	{Helen Thompson Prize for All Round Excellence}
	{St John's College}
	{For academic and extra-curricular contributions.}
\end{entrylist}
\begin{entrylist}
	\entryInline
	{2015} % March 3?
	{IET Student Prize}
	{The Institution of Engineering and Technology}
	{Outstanding academic success.}
\end{entrylist}
\begin{entrylist}
	\entryInline
	{2015} % Feb 6
	{David Andrew Krnak Memorial Prize}
	{University of Queensland}
	{Top engineering graduate.}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2014} % Oct 24
	{UQ Future Leader}
	{University of Queensland}
	{Recognises graduating students who have gone beyond their typical program of studies to make a positive impact on campus and community.}
\end{entrylist}
\begin{entrylist}
	\entryInline
	{2014} % Dec 12?
	{IEEE Student Thesis Prize}
	{IEEE}
	{Best final year thesis.}
\end{entrylist}
\begin{entrylist}
	\entryInline
	{2014}
	{GroundProbe Prize}
	{University of Queensland}
	{Best final year thesis.} % microwave, photonics \& communications..}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2014}
	{RWH Hawken Scholar}
	{University of Queensland}
	{(2010--2014) Awarded to highly performing students}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2014}
	{UQ Summer Research Scholarship}
	{University of Queensland}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2012}
	{Walter Bruce Darker Scholarship}
	{University of Queensland}
	{Top 3rd year engineering student.}
\end{entrylist}
\begin{entrylist}
	\entryInline
	{2012}
	{Exxon Mobil Achievement Award}
	{University of Queensland}
	{Top mechanical engineering student.}
\end{entrylist}
\begin{entrylist}
	\entryInline
	{2011}
	{Alstom Prize}
	{University of Queensland}
	{Top electrical engineering student.}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2010}
	{UQ Academic Excellence Scholarship}
	{University of Queensland}
	{A four year scholarship awarded to students demonstrating high academic ability.}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2010}
	{ICT Enabling Scholarship}
	{University of Queensland}
	{A one year scholarship awarded to students who have demonstrated outstanding Information and Communications Technology skills.}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2010}
	{John Black Prize}
	{University of Queensland}
	{Highest performing first year male.}
\end{entrylist}











%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Communication}

\begin{entrylist}
%------------------------------------------------
\entry
	{2019-2017}
	{\textit{ScopeTV} Guest Scientist}
	{ScopeTV, Channel 10}
	{Helped script, narrate and appear in ScopeTV educational astronomy episodes.}
\end{entrylist}
\begin{entrylist}
\entry
	{2019}
	{\textit{Science Says!} Scientific Panelist}
	{World Science Festival}
	{Panel scientist for Science Says, a comedy science show for Brisbane's World Science Festival.}
\end{entrylist}
\begin{entrylist}
\entry
	{2019}
	{\textit{Probably Science Podcast }Guest Scientist}
	{Probably Science Live Podcast and Comedy Show}
	{Guest scientist for Probably Science, joining the previous guests of Neil deGrasse Tyson, Sean Carroll and more.}
\end{entrylist}
\begin{entrylist}
\entry
	{2019}
	{\textit{2SER Radio} Scientific Correspondent}
	{Radio, 2SER}
	{Monthly scientific and astronomy updates.}
\end{entrylist}
\begin{entrylist}
\entry
    {2018}
    {BrisScience Presenter}
    {BrisScience \& UQ}
    {Invited to talk at the monthly BrisScience event on the dark side of the universe.}
\end{entrylist}
\begin{entrylist}
\entry
    {2018}
    {Australian Survivor Invited Contestant, Academic Champion}
    {Endemol Shine}
    {Cast as the academic champion for the `Champions v. Contendors' season of Australian Survivor.}
\end{entrylist}
\begin{entrylist}
\entry
    {2018-2017}
    {School Guest Presenter}
    {Clayfield College, Gumdale State School}
    {Talks to primary and secondary students on astronomy, science, STEM and career pathways.}
\end{entrylist}
\begin{entrylist}
\entry
   {2019-2017}
   {Science Communicator}
   {Pint of Science, Physics in the Pub}
   {Gave public talks to a general audience about various topics in astronomy.}
\end{entrylist}
\begin{entrylist}
\entry
    {2017}
    {Invited Presenter}
    {Research Education and Development Retreat}
    {Invited presenter at a progressional development program for physics PhD, honours and undergraduate students.}
\end{entrylist}
\begin{entrylist}
\entry
    {2017}
    {Workshop Organiser, Host and Presenter}
    {CAASTRO Code Workshop}
    {Created and presented a code workshop focusing on open-source science run across Australia.}
\end{entrylist}
\begin{entrylist}
\entry
    {2017}
    {Battle of the Brains Panel Scientist}
    {National Science Week}
    {Invited participant in a games panel discussion for physicists during National Science Week.}
\end{entrylist}
\begin{entrylist}
\entry
    {2017}
    {World Science Festival Tour Guide}
    {Queensland Museum \& UQ}
    {Scientific tour guide for the Large Hadron Collider exhibit during the World Science Festival.}
\end{entrylist}
\begin{entrylist}
\entry
    {2017}
    {FameLab Australia Scientist}
    {British Council}
    {State finalist FameLab scientist. Public communication through radio interview and stage presentation.}
\end{entrylist}
\begin{entrylist}
\entry
    {2016}
    {Guest Scientist, An Evening with Dr Lisa Randall}
    {ThinkInc}
    {Gave the opening speech for the Brisbane event, talking about the exciting future of astronomy.}
\end{entrylist}
\begin{entrylist}
\entry
    {2016}
    {UQ Science Demo Troupe Member}
    {University of Queensland}
    {Joined the UQ Science Demo troupe to create resources for the group and participate in UQ demonstrations.}
\end{entrylist}
\begin{entrylist}
\entry
    {2016}
    {Uluru Astronomer in Residence}
    {CAASTRO}
    {Accompanied Sky Tours to answer scientific questions from the public and gave public lectures on popular astronomy topics.}
\end{entrylist}


\section{Teaching}
\begin{entrylist}
	\entryInlineSmall
	{2018}
	{Introduction to Astrophysics Guest Lecturer}
	{University of Queensland}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2018}
	{Cosmology Tutor and Guest Lecturer}
	{University of Queensland}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2018}
	{Supervisor - Capstone Project}
	{University of Queensland}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2017}
	{Computational Physics Tutor}
	{University of Queensland}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2017}
	{Computational Physics Content Creator}
	{University of Queensland}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2017}
	{Supervisor - Summer Project}
	{University of Queensland}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{2015}
	{5-Minute Physics Content Creator}
	{University of Queensland}
	{Created simulations and visualisations.}
\end{entrylist}






\section{Academic Presentations}
\begin{entrylist}
	\entryInlineSmall{July 2019}{Barry - A BAO model fitting framework}{Python in Astronomy}{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall{Mar 2019}{The path towards Photometric Supernova Cosmology with DES}{Cosmology on Safari}{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall{Feb 2019}{Hitting the Limits of Supernova cosmology}{ANITA}{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall{Nov 2017}{Coding Practises for the Busy Astronomer}{CAASTRO}{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{Jun 2017}
	{Hierachical Bayesian Models for Supernova Cosmology}
	{Lawrence Berkeley National Lab}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{Dec 2016}
	{Introduction to git and code management}
	{University of Cambridge}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{Dec 2016}
	{Hierachical Bayesian Models for Supernova Cosmology}
	{University of Southampton}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{Dec 2016}
	{Hierachical Bayesian Models for Supernova Cosmology}
	{University of Portsmouth}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{Nov 2016}
	{Sound waves in Space: Wigglez and the BAO}
	{Swinburne University of Technology}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{Aug 2016}
	{Publishing Packages in Python}
	{University of Queensland}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{Aug 2016}
	{ChainConsumer: Plots and LaTeX from MCMC chains}
	{CAASTRO}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{May 2016}
	{Hieracrhical Bayesian Models for Supernova Cosmology}
	{Standford University}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{Feb 2016}
	{Detecting Globular Clusters in Maffei 1}
	{Gemini Institute}
	{}
\end{entrylist}
\begin{entrylist}
	\entryInlineSmall
	{Nov 2015}
	{Marz - Redshifting software inside your browser}
	{OzDES Workshop}
	{}
\end{entrylist}











\section{Publications}


\subsection{Primary Author}

\newrefcontext[sorting=ydnt]
\begin{refsection}
    \nocite{*}
    \printbibliography[heading=none, keyword={primary}]
\end{refsection}


\subsection{Contributing Author}
\begin{refsection}
	\nocite{*}
	\printbibliography[heading=none, keyword={secondary}]
\end{refsection}


\subsection{In Journal Review}
\begin{refsection}
	\nocite{*}
	\printbibliography[heading=none, keyword={draft}]
\end{refsection}

%\printbibsection{article}{Articles}{primary} % Print all articles from the bibliography
%\printbibsection{article}{Articles}{secondary}

%\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

%\printbibsection{report}{research reports} % Print all research reports from the bibliography
%\begin{entrylist}
%------------------------------------------------

%------------------------------------------------
%\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------



%%
%\clearpage
%\section{Referees}
%\begin{entrylist}
%\entry
%{Cosmology}
%{Prof. Tamara Davis}
%{Physics Department, University of Queensland}
%{Tamara Davis is an Australian Research Council Future Fellow and researches fundamental physics, such as the properties of dark matter and dark energy.\\Contactable at 0432 526 989 \& tamarad@physics.uq.edu.au.}
%\end{entrylist}
%\begin{entrylist}
%\entry
%{Cosmology}
%{Prof. Michael Drinkwater}
%{Physics Department, University of Queensland}
%{Michael Drinkwater obtained his PhD in Cambridge and currently holds position in the University of Queensland's Physics Department as a Professor of Astrophysics.\\Contactable at 0432 887 642 \& m.drinkwater@uq.edu.au.}
%\end{entrylist}


\end{document}